\ifdefined\english

    \section*{Employment}

    \noindent\textbf{A quantitative trading firm~\footnote{A Shanghai-based quantitative trading firm with assets under management (AUM) over 10 billion CNY.} \textbar{} Quantitative Developer (2025.04 - Present)} \hfill \textsl{Permanent}

    \noindent\textbf{\phantom{A quantitative trading firm~\footnote{}} \textbar{} Quantitative Developer (2024.08 - 2024.11)} \hfill \textsl{Summer Intern}

    \begin{itemize}
        \item Participated in the development of a trading platform and simulation system; responsible for data integration with brokers and trading desks; maintained the stability and reliability of the live trading and strategy simulation environments.
        \item Participated in strategy development to improve the performance, stability, and profitability of trading strategies; Increased the query speed of the trading platform snapshot index by 4.3 times.
    \end{itemize}

    \noindent\textbf{\href{https://www.alibabacloud.com}{Alibaba Cloud} \textbar{} Infrastructure - Storage - \href{https://www.alibabacloud.com/en/product/object-storage-service}{Object Storage Service (OSS)}~\footnote{OSS is a core business of Alibaba Cloud, holding the largest market share in China and ranking second globally, just behind AWS S3.} \textbar{} Intern (2024.05 - 2024.07)} \hfill \textsl{Summer Intern}

    \begin{itemize}
        \item Developed a Rust SDK for the OSS team to provide customers with a complete development toolkit for using OSS services.
        \item Independently developed a prototype that includes basic API implementations and extended API feature modules. The codebase consists of 15K lines, with a CodeCov of 94\%, and complete documentation.
    \end{itemize}

    \noindent\textbf{\href{https://blocksec.com}{BlockSec} \textbar{} Audit Development Team \& Vulnerability Analysis Team \textbar{} Research Intern (2021.09 - 2024.01)} \hfill \textsl{Research Intern}

    \begin{itemize}
        \item Independently developed Rustle, an automated audit tool for Rust smart contracts based on static analysis.
        \item Contributed to the development of automated audit tool Anshun for Ethereum smart contracts.
        \item Independently established the company's contract vulnerability alert system and participated in the company's vulnerability response efforts.
    \end{itemize}

    \noindent\textbf{\href{https://300188.cn}{SDIC Intelligence (Meiya Pico)} \textbar{} Institute of Electronic Data Forensics and Intelligent Equipment Research AI Development Center \textbar{} Algorithm Engineer Intern (2020.07 - 2020.08)} \hfill \textsl{Daily Intern}

    \begin{itemize}
        \item Developed algorithms to identify possible image tampering. The functionality has been integrated into the company's product.
    \end{itemize}

\else

    \section*{工作经历}

    \noindent\textbf{上海某百亿量化私募 \textbar{} 量化开发 (2025.04 - 至今)} \hfill \textsl{全职}

    \noindent\textbf{\phantom{上海某百亿量化私募} \textbar{} 量化开发 (2024.08 - 2024.11)} \hfill \textsl{暑期实习}

    \begin{itemize}
        \item 参与交易平台和回测系统的开发；负责与券商和柜台的数据对接；维护实盘交易及策略回测环境的稳定性与可靠性
        \item 参与策略开发工作，提升交易策略的性能、稳定性及收益率；将交易平台快照索引的查询速度提升 4.3 倍
    \end{itemize}

    \noindent\textbf{\href{https://www.aliyun.com}{阿里云} \textbar{} 基础设施事业部 - 存储 - \href{https://www.aliyun.com/product/oss}{对象存储 (OSS)}~\footnote{对象存储是阿里云的核心业务，市场份额居中国首位，全球排名第二，仅次于 AWS S3。} \textbar{} 实习生 (2024.05 - 2024.07)} \hfill \textsl{暑期实习}

    \begin{itemize}
        \item 为 OSS 团队开发 Rust SDK，向客户提供使用 OSS 服务的完整开发套件，客户无需关心服务端 API 参数细节即可与之高效交互
        \item 独立开发原型，包含基础 API 实现及拓展 API 功能模块；代码量 15K，CodeCov 94\%，文档完整
    \end{itemize}

    \noindent\textbf{\href{https://blocksec.com}{BlockSec} \textbar{} 审计平台开发团队 \& 漏洞攻击分析团队 \textbar{} 科研实习生 (2021.09 - 2024.01)} \hfill \textsl{科研实习}

    \begin{itemize}
        \item 独立开发针对 Rust 智能合约，基于静态分析的自动化审计工具 Rustle
        \item 参与团队开发针对以太坊智能合约的自动化审计工具 Anshun
        \item 独立搭建公司的合约漏洞预警系统，参与公司的漏洞响应工作
    \end{itemize}

    \noindent\textbf{\href{https://300188.cn}{国投智能（美亚柏科）} \textbar{} 电子数据取证与智能装备研究院 \textbar{} 算法工程师实习生 (2020.07 - 2020.08)} \hfill \textsl{日常实习}

    % 电子数据取证与智能装备研究院 AI 研发中心

    \begin{itemize}
        \item 针对电子取证过程中可能存在的图像伪造问题进行识别。通过复现图形学算法，能够准确地检测出图像中难以察觉的拼贴、剪切、拖移、消除等后期处理手段；该功能已成功集成到美亚柏科的电子取证平台
    \end{itemize}

\fi

\hfill
